Polytope notes

### 2020-01-23 notes/polytope-notes.tex
Redoing the only if proof on the feasibility of the QP

    \bigskip
    $\impliedby$
    Suppose there was a feasible solution to the quadratic program above.
    We claim that $\T$ such that $T_y = \conv(\{x_{1y}, \ldots, x_{\ell y} \})$ \jessiet{Tried with these polytopes since they guarantee polytopes, but I can't see where $\{x : Vx \leq B_{;y}\}$ guarantees boundedness...} forms a valid set of polytopes so that $D^\T = C$, and therefore we satisfy our optimality condition by Proposition~\ref{prop:relate-E-B}.

    To see $C \subseteq D^\T$, take some $p \not \in D^\T$.
    We then have $\vec 0 \not \in \oplus_y p_y T_y$, which in turn implies that, for al\jessiet{this quantifier seems really important, but I'm not confident it's correct.} $j \in [\ell]$, there are no witnesses $\bar x_{jy}$ so that $\sum_y p^j_y \bar x_{jy} = 0$.
    If $p \in C$, then we contradict our feasibility constraints, so we conclude that we must have $p \not \in C$.
    Thus, we have $C \subseteq D^\T$.

>>>>

    \bigskip
    $\impliedby$
    Suppose there was a feasible solution to the quadratic program above.
    We claim that $\T$ such that $T_y = \conv(\{x_{1y}, \ldots, x_{\ell y} \})$ \jessiet{Tried with these polytopes since they guarantee polytopes, but I can't see where $\{x : Vx \leq B_{;y}\}$ guarantees boundedness... also don't see where to use the first statement of the QP in the proof though, since we don't get the normals of the convex hull necessarily being the normals found by the QP.} forms a valid set of polytopes so that $D^\T = C$, and therefore we satisfy our optimality condition by Proposition~\ref{prop:relate-E-B}.

    To see $C \subseteq D^\T$, take $\bar p \in C = \conv(\{p^1, \ldots, p^\ell\})$.
    Then there exists $\lambda \in \Delta_{\ell}$ so that $\bar p = \sum_j \lambda_j p^j$, and in turn, $\bar p_y = \sum_j \lambda_j p^j_y$.
    By satisfying the quadratic program, we know that 
    \begin{align*}
    \sum_y p^j_y x_{jy} &= 0 \;\; \forall j \in [\ell]\\
    \sum_j \sum_y p^j_y x_{jy} &= 0\\
    \sum_y \sum_j p^j_y x_{jy} &= 0\\
    \sum_y \sum_j \lambda_j p^j_y x_{jy} &= 0\\
    \sum_y \sum_j \bar p_y x_{jy} &= 0\\
    \sum_y \bar x_y &= 0 
    \end{align*}
    where $\bar x_y := \sum_j \bar p_y x_{jy} \in \conv(\{x_{1y}, \ldots, x_{\ell y}\}) = T_y$ for all $y \in [n]$.
    As $\bar x$ is a witness that $\vec 0 \in \oplus_y \bar p_y T_y$, we have $\bar p \in D^\T$, thus $C\subseteq D^\T$.
%    To see $C \subseteq D^\T$, take some $p \not \in D^\T$.
%    We then have $\vec 0 \not \in \oplus_y p_y T_y$, which in turn implies that, for al\jessiet{this quantifier seems really important, but I'm not confident it's correct.} $j \in [\ell]$, there are no witnesses $\bar x_{jy}$ so that $\sum_y p^j_y \bar x_{jy} = 0$.
%    If $p \in C$, then we contradict our feasibility constraints, so we conclude that we must have $p \not \in C$.
%    Thus, we have $C \subseteq D^\T$.
